---
title: "Lab 01 - Hello R"
author: "Lilly McClendon"
date: "01-22-2025"
output: 
  html_document: 
    fig_height: 4
    fig_width: 9
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)

datasaurus_dozen %>%
  count(dataset) %>%
  print(13)

```

## Exercises

### Exercise 1

The datasaurus_dozen file contains 1846 rows and 3 columns. The variables in the data frame are the dataset the data are from, and the x and y values.  

### Exercise 2

Plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
```
###Visualize the data 
```{r plot-dino, fig.height=3, fig.width=6}
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

Some pairs of the variables do not have a linear relationship. Therefore, you first visualize the data so that you can determine if there is a non-linear relationship. If there is a nonlinear relationship, you do not calculate the correlation coefficient (r). 

### Exercise 3

This is your turn to write the code and narrative for the star dataset. Follow the same steps as above to complete the analysis. Don't forget to label your chunks appropriately!

Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.
To finish, clean up the narrative by removing these instructions.

```{r plot-star}
library(tidyverse) 
library(plot-star)

plot-star %>%
  count(dataset) %>%
  print(13)
```

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
```

###Visualize the data 
```{r plot-star, fig.height=3, fig.width=6}
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


I'm some filler text, you should replace me with more meaningful text...

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
Add your explanation here—what did you notice?


### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r}

```

```{r}

```

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


