---
title: "Lab 01 - Hello R"
author: "Lilly McClendon"
date: "01-22-2025"
output: 
  html_document: 
    fig_width: 6
    highlight: kate
    theme: cerulean
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)

datasaurus_dozen %>%
  count(dataset) %>%
  print(13)

```

## Exercises

### Exercise 1

The datasaurus_dozen file contains 1846 rows and 3 columns. The variables in the data frame are the dataset the data are from, and the x and y values.  

### Exercise 2

#### Plot the dino data in the dino dataset:
```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
```

#### Visualize the dino data 
```{r plot-dino2, fig.height=3, fig.width=6}
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#### Calculate the correlation between `x` and `y` in this dataset:
```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

Some pairs of the variables do not have a linear relationship. Therefore, you first visualize the data so that you can determine if there is a non-linear relationship. If there is a nonlinear relationship, you do not calculate the correlation coefficient (r). 

### Exercise 3

#### Plot the star data in the dataset 
```{r plot-star, fig.height=3, fig.width=3}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
```

#### Visualize the star data 
```{r visualize-star, fig.height=3, fig.width=3}
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#### Calculate the correlation between `x` and `y` in the star data:
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient (measure of strength and direction of a linear relationship between two variables) of the dinosaur and the star are both around -0.06 which as it is close to zero indicates almost no correlation. Despite being more angular, the star also does not have a linear relationship. The data in the dinosaur when plotted forms curved lines while the star consists of more straight lines. However, the correlation coefficient (r) of the dionsaur and the star are quite similar. 


### Exercise 4

#### Plot the circle data in the dataset 
```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
```

#### Visualize the circle data 
```{r visualize-circle2, fig.height=4, fig.width=4}
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
#### Calculate the correlation between `x` and `y` in the circle data:
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
The r value of the circle data is -0.07 which is quite similar to the r value of the dino data which was -0.06. Both the r values indicate there is almost no correlation between the two variables. 

### Exercise 5

#### Facet by the dataset variable 
```{r facet, fig.height=5, fig.width=3}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```
#### Generate summary correlation coefficients
```{r summary-correlation-coefficients}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
## Emojis 

### Install emoji package 
```{r install emo package}
#install.packages("emo")
```

### Search emoji 
```{r search emoji}
library(emojifont)
search_emoji('smile')
```

### Use emoji 
```{r use emoji}
cat("This is the end of Lab 01!", emoji("smiley_cat") )
```
